Titulo

### 2014-10-29 RotacionOutFlows/Paper/ms.tex
more paper

\section{Theoretical Frame}
\label{sec:theo}
In this section we are going to describe the two different models that are used in this project, that are able to reproduce a real and consistent line.\\

@@

---------------------------------------------------------------------\\
MISSING: \\
- What are the compact results.\\
- Some plots.\\
- Not a physical analysis yet. \\
- Write 
-----------------------------------------------------------------------\\

@@

@@

>>>>

\section{Theoretical Frame}
\label{sec:theo}
In this section we are going to describe the two different models that are used in this project, that are able to reproduce a real and consistent \lya profile.\\

@@

---------------------------------------------------------------------\\
MISSING: \\
- What are the compact results.\\
- Some plots.\\
- Not a physical analysis yet. \\
- Write better (prettier)\\
-----------------------------------------------------------------------\\

@@

---------------------------------------------------------------------\\
MISSING: \\
- Figure that explains better.\\
-----------------------------------------------------------------------\\

@@

\subsubsection{Influence of the Outflow Expanding Velocity: \vel }

---------------------------------------------------------------------\\
MISSING: \\
- Influence Outflow Velocity.\\
-----------------------------------------------------------------------\\
